D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-24 ootavacuous.tex
Change "vs." to "versus"
To be consistent with the title of section 6.4.2, change the title of
section 2.1 to "OOTA: rf versus rfe".  Besides, "rf" and "rfe" are
already acronyms so the title doesn't really need another abbreviation.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Section~\ref{sec:OOTA: rf vs. rfe}
demonstrates advantages of formulating an OOTA cycle as a cycle in
sdep $\cup$ rfe instead of the traditional sdep $\cup$ rf.
Section~\ref{sec:Properties of Semantic Dependencies}
then discusses properties of semantic dependences, showing that they
are functions of executions rather than strictly of source code,
among other things.

\subsection{OOTA: rf vs.\ rfe}
\label{sec:OOTA: rf vs. rfe}

@@

Listings~\ref{lst:OOTA With an Intrathread Store-Load Link}
and~\ref{lst:OOTA With an Intrathread Store-Load Link, Optimized}
show the examples from
Section~\ref{sec:OOTA: rf vs. rfe}
in the form of litmus tests.
A compiler is allowed to transform the program in
Listing~\ref{lst:OOTA With an Intrathread Store-Load Link}
to the form of
Listing~\ref{lst:OOTA With an Intrathread Store-Load Link, Optimized},
which demonstrates that intrathread reads-from (rfi) links may be
eliminated by the compiler and therefore should not be used in a
definition of OOTA.
This section provides a more involved example to drive the point home.

>>>>

Section~\ref{sec:OOTA: rf versus rfe}
demonstrates advantages of formulating an OOTA cycle as a cycle in
sdep $\cup$ rfe instead of the traditional sdep $\cup$ rf.
Section~\ref{sec:Properties of Semantic Dependencies}
then discusses properties of semantic dependences, showing that they
are functions of executions rather than strictly of source code,
among other things.

\subsection{OOTA: rf versus rfe}
\label{sec:OOTA: rf versus rfe}

@@

Listings~\ref{lst:OOTA With an Intrathread Store-Load Link}
and~\ref{lst:OOTA With an Intrathread Store-Load Link, Optimized}
show the examples from
Section~\ref{sec:OOTA: rf versus rfe}
in the form of litmus tests.
A compiler is allowed to transform the program in
Listing~\ref{lst:OOTA With an Intrathread Store-Load Link}
to the form of
Listing~\ref{lst:OOTA With an Intrathread Store-Load Link, Optimized},
which demonstrates that intrathread reads-from (rfi) links may be
eliminated by the compiler and therefore should not be used in a
definition of OOTA.
This section provides a more involved example to drive the point home.
